### 2022-01-28 .debris/2022-01-27 11.57.22.00/Paper.tex
modified

\section{Non-linear rheologies}\label{sec:nonlinear}
Non-linear rheologies are implemented combining viscous creep (dislocation and diffusion) and plastic yielding. For each marker, diffusion and dislocation
viscosity ($\eta_{df|ds}$) can be determined as follows \citep{Karato1993,Wang2016}:
\begin{equation}\label{eq:viscous}
\eta_{df|ds}=\left(\frac{d^m}{A}\right)^{\frac{1}{n}}I_2^{\frac{(1-n)}{n}}\exp\left(\frac{Q+pV}{nRT}\right)
\end{equation}
where $d$ is the grain size, $m$ is the grain size exponent, $n$ is the stress exponent, $A$ is the un9i-axial pre-exponential factor, $I_2$ is the square root of
the second invariant of the strain rate tensor, $Q$ is the activation energy, $p$ is the pressure, $V$ is the activation volume, $R$ is the gas constant and $T$
is the temperature. Pressures and temperatures are determined by the interpolation of the nodal parameters, while strain rates are calculated by means of the
derivative of the velocities on the nodes. In case of diffusion creep $n=1$ and $m>0$, in case of dislocation creep $n>1$ and $m=0$. The viscous creep $\eta_{cp}$
is then calculated as the harmonic average between $\eta_{df}$ and $\eta_{ds}$:
\begin{equation}\label{eq:visco_creep}
\eta_{cp}=\left(\frac{1}{\eta_{df}}+\frac{1}{\eta_{ds}}\right)^{-1}
\end{equation}
The implementation of the non-linear viscous creep viscosity depending on the strain rate is tested by means of the slab detachment benchmark
(Section \ref{sec:slab}).

>>>>

\section{Non-linear rheologies}\label{sec:nonlinear}
Non-linear rheologies are implemented combining viscous creep (dislocation and diffusion) and plastic yielding. For each marker, diffusion and dislocation
viscosity ($\eta_{df|ds}$) can be determined as follows \citep{Karato1993,Wang2016}:
\begin{equation}\label{eq:viscous}
\eta_{df|ds}=\left(\frac{d^m}{A}\right)^{\frac{1}{n}} 2^{\frac{1-n}{2n}} I_2^{\frac{(1-n)}{n}}\exp\left(\frac{Q+pV}{nRT}\right)
\end{equation}
where $d$ is the grain size, $m$ is the grain size exponent, $n$ is the stress exponent, $A$ is the uniaxial pre-exponential factor, $I_2$ is the square root of
the second invariant of the strain rate tensor, $Q$ is the activation energy, $p$ is the pressure, $V$ is the activation volume, $R$ is the gas constant and $T$
is the temperature. Pressures and temperatures are determined by the interpolation of the nodal parameters, while strain rates are calculated by means of the
derivative of the velocities on the nodes. In case of diffusion creep $n=1$ and $m>0$, in case of dislocation creep $n>1$ and $m=0$. The viscous creep $\eta_{cp}$
is then calculated as the harmonic average between $\eta_{df}$ and $\eta_{ds}$:
\begin{equation}\label{eq:visco_creep}
\eta_{cp}=\left(\frac{1}{\eta_{df}}+\frac{1}{\eta_{ds}}\right)^{-1}
\end{equation}
The implementation of the non-linear viscous creep viscosity depending on the strain rate is tested by means of the slab detachment benchmark
(Section \ref{sec:slab}).

### 2022-01-28 .debris/2022-01-27 12.02.23.00/Paper.tex
modified

\section{Non-linear rheologies}\label{sec:nonlinear}
Non-linear rheologies are implemented combining viscous creep (dislocation and diffusion) and plastic yielding. For each marker, diffusion and dislocation
viscosity ($\eta_{df|ds}$) can be determined as follows \citep{Karato1993,Wang2016}:
\begin{equation}\label{eq:viscous}
\eta_{df|ds}=\left(\frac{d^m}{A}\right)^{\frac{1}{n}} 2^{\frac{1-n}{2n}} I_2^{\frac{(1-n)}{n}}\exp\left(\frac{Q+pV}{nRT}\right)
\end{equation}
where $d$ is the grain size, $m$ is the grain size exponent, $n$ is the stress exponent, $A$ is the uniaxial pre-exponential factor, $I_2$ is the square root of
the second invariant of the strain rate tensor, $Q$ is the activation energy, $p$ is the pressure, $V$ is the activation volume, $R$ is the gas constant and $T$
is the temperature. Pressures and temperatures are determined by the interpolation of the nodal parameters, while strain rates are calculated by means of the
derivative of the velocities on the nodes. In case of diffusion creep $n=1$ and $m>0$, in case of dislocation creep $n>1$ and $m=0$. The viscous creep $\eta_{cp}$
is then calculated as the harmonic average between $\eta_{df}$ and $\eta_{ds}$:
\begin{equation}\label{eq:visco_creep}
\eta_{cp}=\left(\frac{1}{\eta_{df}}+\frac{1}{\eta_{ds}}\right)^{-1}
\end{equation}
The implementation of the non-linear viscous creep viscosity depending on the strain rate is tested by means of the slab detachment benchmark
(Section \ref{sec:slab}).

>>>>

\section{Non-linear rheologies}\label{sec:nonlinear}
Non-linear rheologies are implemented combining viscous creep (dislocation and diffusion) and plastic yielding. For each marker, diffusion and dislocation
viscosity ($\eta_{df|ds}$) can be determined as follows \citep{Karato1993,Wang2016}:
\begin{equation}\label{eq:viscous}
\eta_{df|ds}=f_s \left(\frac{d^m}{A}\right)^{\frac{1}{n}} \frac{2^{\frac{1-n}{n}}}{3^{\frac{n+1}{2n}}} I_2^{\frac{(1-n)}{n}}\exp\left(\frac{Q+pV}{nRT}\right)
\end{equation}
where $f_s$ is a scaling factor used to represent lithologies that are stronger or weaker than the base set, $d$ is the grain size, $m$ is the grain size exponent,
$n$ is the stress exponent, $A$ is the uniaxial pre-exponential factor, $I_2$ is the square root of the second invariant of the strain rate tensor, $Q$ is the
activation energy, $p$ is the pressure, $V$ is the activation volume, $R$ is the gas constant and $T$ is the temperature.
Pressures and temperatures are determined by the interpolation of the nodal parameters, while strain rates are calculated by means of the
derivative of the velocities on the nodes. In case of diffusion creep $n=1$ and $m>0$, in case of dislocation creep $n>1$ and $m=0$. The viscous creep $\eta_{cp}$
is then calculated as the harmonic average between $\eta_{df}$ and $\eta_{ds}$:
\begin{equation}\label{eq:visco_creep}
\eta_{cp}=\left(\frac{1}{\eta_{df}}+\frac{1}{\eta_{ds}}\right)^{-1}
\end{equation}
The implementation of the non-linear viscous creep viscosity depending on the strain rate is tested by means of the slab detachment benchmark
(Section \ref{sec:slab}).

### 2022-01-28 .debris/2022-01-27 12.30.55.00/Paper.tex
modified

\section{Introduction}\label{sec:intro}
This supplement includes a description of the code, with a presentation of the features implemented followed by results of extensive benchmarks listed in
Table \ref{tab:list}, implemented to verify that the code solves correctly a large range of problems. Description and results of all benchmarks are shown
in Section \ref{sec:benchmark}.

>>>>

\section{Introduction}\label{sec:intro}
This document includes a description of the code, with a presentation of the features implemented followed by results of extensive benchmarks listed in
Table \ref{tab:list}, implemented to verify that the code solves correctly a large range of problems. Description and results of all benchmarks are shown
in Section \ref{sec:benchmark}.

### 2022-01-28 .debris/2022-01-27 13.15.54.00/Paper.tex
modified

\section{Introduction}\label{sec:intro}
This document includes a description of the code, with a presentation of the features implemented followed by results of extensive benchmarks listed in
Table \ref{tab:list}, implemented to verify that the code solves correctly a large range of problems. Description and results of all benchmarks are shown
in Section \ref{sec:benchmark}.

>>>>

\section{Introduction}\label{sec:intro}
This document includes a description of the code FALCON, with a presentation of the features implemented followed by results of extensive benchmarks listed in
Table \ref{tab:list}, implemented to verify that the code solves correctly a large range of problems. Description and results of all benchmarks are shown
in Section \ref{sec:benchmark}.

### 2022-01-28 .debris/2022-01-27 13.19.32.00/Paper.tex
modified

\section{Erosion and sedimentation}\label{sec:erosion}
Surface processes at either the lithosphere-air interface or in correspondence of the free surface have been implemented by means of the software
Fastscape\footnote{\url{https://fastscape.org/}} \citep{Braun2013,Cordonnier2019,Yuan2019a,Yuan2019b}.FastScapeLib is a set of routines that solve the stream
power law (enriched by a sediment transport/deposition term) \citep{Yuan2019a}, hillslope diffusion and marine transport and deposition \citep{Yuan2019b}.
The partial differential equation solved by FastScapeLib is:
\begin{equation}
\frac{\partial h}{ \partial t}=U-K_f A^{m_e}S^{n_e} + \frac{G}{A}\int_A \left( U-\frac{\partial h}{\partial t} \right) dA + K_d \bm{\nabla}^2 h 
\end{equation}
where $h$ is the topography, $U$ is the uplift, $K_f$ is the erodibility coefficient, $A$ is the upstream drainage area, $S$ is the slope, $m_e$ and $n_e$ are
parameters that should be chosen to constrain the ratio $m_e/n_e$ between 0.35 and 0.8 \citep{Croissant2014,Ueda2015,Beucher2020}, $G$ is the dimensionless
deposition/transport coefficient for the enriched stream power law and $K_d$ is the effective diffusivity. Terms $$K_f A^{m_e}S^{n_e}$$ and $$K_d \bm{\nabla}^2 h$$
consider long-range processes described by a stream power law equation \citep{Tucker1999,Ueda2015,Beucher2020} and short-range processes are
proportional to slope \citep{Burov1997,Ueda2015,Beucher2020}.

>>>>

\section{Erosion and sedimentation}\label{sec:erosion}
Surface processes at either the lithosphere-air interface or in correspondence of the free surface have been implemented by means of the software
Fastscape\footnote{\url{https://fastscape.org/}} \citep{Braun2013,Cordonnier2019,Yuan2019a,Yuan2019b}. FastScapeLib is a set of routines that solve the stream
power law (enriched by a sediment transport/deposition term) \citep{Yuan2019a}, hillslope diffusion and marine transport and deposition \citep{Yuan2019b}.
The partial differential equation solved by FastScapeLib is:
\begin{equation}
\frac{\partial h}{ \partial t}=U-K_f A^{m_e}S^{n_e} + \frac{G}{A}\int_A \left( U-\frac{\partial h}{\partial t} \right) dA + K_d \bm{\nabla}^2 h 
\end{equation}
where $h$ is the topography, $U$ is the uplift, $K_f$ is the erodibility coefficient, $A$ is the upstream drainage area, $S$ is the slope, $m_e$ and $n_e$ are
parameters that should be chosen to constrain the ratio $m_e/n_e$ between 0.35 and 0.8 \citep{Croissant2014,Ueda2015,Beucher2020}, $G$ is the dimensionless
deposition/transport coefficient for the enriched stream power law and $K_d$ is the effective diffusivity. Terms $$K_f A^{m_e}S^{n_e}$$ and $$K_d \bm{\nabla}^2 h$$
consider long-range processes described by a stream power law equation \citep{Tucker1999,Ueda2015,Beucher2020} and short-range processes are
proportional to slope \citep{Burov1997,Ueda2015,Beucher2020}.

### 2022-01-28 .debris/2022-01-27 13.27.16.00/Paper.tex
modified

\section{Non-linear rheologies}\label{sec:nonlinear}
Non-linear rheologies are implemented combining viscous creep (dislocation and diffusion) and plastic yielding. For each marker, diffusion and dislocation
viscosity ($\eta_{df|ds}$) can be determined as follows \citep{Karato1993,Wang2016}:
\begin{equation}\label{eq:viscous}
\eta_{df|ds}=f_s \left(\frac{d^m}{A}\right)^{\frac{1}{n}} \frac{2^{\frac{1-n}{n}}}{3^{\frac{n+1}{2n}}} I_2^{\frac{(1-n)}{n}}\exp\left(\frac{Q+pV}{nRT}\right)
\end{equation}
where $f_s$ is a scaling factor used to represent lithologies that are stronger or weaker than the base set, $d$ is the grain size, $m$ is the grain size exponent,
$n$ is the stress exponent, $A$ is the uniaxial pre-exponential factor, $I_2$ is the square root of the second invariant of the strain rate tensor, $Q$ is the
activation energy, $p$ is the pressure, $V$ is the activation volume, $R$ is the gas constant and $T$ is the temperature.
Pressures and temperatures are determined by the interpolation of the nodal parameters, while strain rates are calculated by means of the
derivative of the velocities on the nodes. In case of diffusion creep $n=1$ and $m>0$, in case of dislocation creep $n>1$ and $m=0$. The viscous creep $\eta_{cp}$
is then calculated as the harmonic average between $\eta_{df}$ and $\eta_{ds}$:
\begin{equation}\label{eq:visco_creep}
\eta_{cp}=\left(\frac{1}{\eta_{df}}+\frac{1}{\eta_{ds}}\right)^{-1}
\end{equation}
The implementation of the non-linear viscous creep viscosity depending on the strain rate is tested by means of the slab detachment benchmark
(Section \ref{sec:slab}).

@@

\subsection{Viscoplastic mantle convection}\label{sec:visco_mantle}
This benchmark is performed as Cases 1-5a described in \citet{Tosi2015} in a 2D unit square domain with two different grid resolutions of \num{32x32} 
and \num{100x100} elements. Reference viscosity, reference density, heat capacity, thermal conductivity and thermal expansion coefficient are fixed to a constant
value of 1 ($\eta_0= \rho_0= C_p = k=\alpha=1$), while the gravity has been chosen as $g_y=10^2$, in order to obtain a Rayleigh number $Ra=10^2$. Temperatures
are set to 0 on top and 1 on bottom of the domain. Velocity boundary conditions are set to free slip on all sides. The initial temperature field is given by
\[T(x,y)=(1-y)+0.01 \cos (\pi x) \sin (\pi y)\].
The viscosity ﬁeld $\eta$ is calculated as the harmonic average between a linear part $\eta_{lin}$ that depends on temperature only or on temperature and 
depth $y$ and a nonlinear-plastic part $\eta_{pl}$ that depends on the strain rate $\dot{\bm{\epsilon}}$, as follows
\[\eta(T,y,\dot{\bm{\epsilon}})=2\left(\frac{1}{\eta_{lin}(T,y)}+\frac{1}{\eta_{pl}(\dot{\bm{\epsilon}})}\right)^{-1}\]
The linear and the nonlinear-plastic parts of the viscosity are calculated following \citet{Tosi2015} as follows
\[\eta_{lin}(T,y)=\exp(-\ln(\Delta\eta_T)T+\ln(\Delta\eta_y)y)\]
\[\eta_{pl}(\dot{\bm{\epsilon}})=\eta^*+\frac{\sigma_Y}{\sqrt{\dot{\bm{\epsilon}}:\dot{\bm{\epsilon}}}}\]
where $\Delta\eta_T$, $\Delta\eta_y$, $\eta^*$ and $\sigma_Y$ are parameters chosen as listed in Table \ref{tab:tosi_setup}.

>>>>

\section{Non-linear rheologies}\label{sec:nonlinear}
Non-linear rheologies are implemented combining viscous creep (dislocation and diffusion) and plastic yielding. For each marker, diffusion and dislocation
viscosity ($\eta_{df|ds}$) can be determined as follows \citep{Karato1993,Wang2016}:
\begin{equation}\label{eq:viscous}
\eta_{df|ds}=f_s \left(\frac{d^m}{A}\right)^{\frac{1}{n}} \left (\frac{2^{\frac{1-n}{n}}}{3^{\frac{n+1}{2n}}} \right)
I_2^{\frac{(1-n)}{n}}\exp\left(\frac{Q+pV}{nRT}\right)
\end{equation}
where $f_s$ is a scaling factor used to represent lithologies that are stronger or weaker than the base set, $d$ is the grain size, $m$ is the grain size exponent,
$n$ is the stress exponent, $A$ is the uniaxial pre-exponential factor, $I_2$ is the square root of the second invariant of the strain rate tensor, $Q$ is the
activation energy, $p$ is the pressure, $V$ is the activation volume, $R$ is the gas constant and $T$ is the temperature.
Pressures and temperatures are determined by the interpolation of the nodal parameters, while strain rates are calculated by means of the
derivative of the velocities on the nodes. In case of diffusion creep $n=1$ and $m>0$, in case of dislocation creep $n>1$ and $m=0$. The viscous creep $\eta_{cp}$
is then calculated as the harmonic average between $\eta_{df}$ and $\eta_{ds}$:
\begin{equation}\label{eq:visco_creep}
\eta_{cp}=\left(\frac{1}{\eta_{df}}+\frac{1}{\eta_{ds}}\right)^{-1}
\end{equation}
The implementation of the non-linear viscous creep viscosity depending on the strain rate is tested by means of the slab detachment benchmark
(Section \ref{sec:slab}).

@@

\subsection{Viscoplastic mantle convection}\label{sec:visco_mantle}
This benchmark is performed as Cases 1-5a described in \citet{Tosi2015} in a 2D unit square domain with two different grid resolutions of \num{32x32} 
and \num{100x100} elements. Reference viscosity, reference density, heat capacity, thermal conductivity and thermal expansion coefficient are fixed to a constant
value of 1 ($\eta_0= \rho_0= C_p = k=\alpha=1$), while the gravity has been chosen as $g_y=10^2$, in order to obtain a Rayleigh number $Ra=10^2$. Temperatures
are set to 0 on top and 1 on bottom of the domain. Velocity boundary conditions are set to free slip on all sides. The initial temperature field is given by
\[T(x,y)=(1-y)+0.01 \cos (\pi x) \sin (\pi y)\].
The viscosity field $\eta$ is calculated as the harmonic average between a linear part $\eta_{lin}$ that depends on temperature only or on temperature and 
depth $y$ and a nonlinear-plastic part $\eta_{pl}$ that depends on the strain rate $\dot{\bm{\epsilon}}$, as follows
\[\eta(T,y,\dot{\bm{\epsilon}})=2\left(\frac{1}{\eta_{lin}(T,y)}+\frac{1}{\eta_{pl}(\dot{\bm{\epsilon}})}\right)^{-1}\]
The linear and the nonlinear-plastic parts of the viscosity are calculated following \citet{Tosi2015} as follows
\[\eta_{lin}(T,y)=\exp(-\ln(\Delta\eta_T)T+\ln(\Delta\eta_y)y)\]
\[\eta_{pl}(\dot{\bm{\epsilon}})=\eta^*+\frac{\sigma_Y}{\sqrt{\dot{\bm{\epsilon}}:\dot{\bm{\epsilon}}}}\]
where $\Delta\eta_T$, $\Delta\eta_y$, $\eta^*$ and $\sigma_Y$ are parameters chosen as listed in Table \ref{tab:tosi_setup}.

### 2022-01-28 .debris/2022-01-27 14.29.51.00/Paper.tex
modified

\section{Erosion and sedimentation}\label{sec:erosion}
Surface processes at either the lithosphere-air interface or in correspondence of the free surface have been implemented by means of the software
Fastscape\footnote{\url{https://fastscape.org/}} \citep{Braun2013,Cordonnier2019,Yuan2019a,Yuan2019b}. FastScapeLib is a set of routines that solve the stream
power law (enriched by a sediment transport/deposition term) \citep{Yuan2019a}, hillslope diffusion and marine transport and deposition \citep{Yuan2019b}.
The partial differential equation solved by FastScapeLib is:
\begin{equation}
\frac{\partial h}{ \partial t}=U-K_f A^{m_e}S^{n_e} + \frac{G}{A}\int_A \left( U-\frac{\partial h}{\partial t} \right) dA + K_d \bm{\nabla}^2 h 
\end{equation}
where $h$ is the topography, $U$ is the uplift, $K_f$ is the erodibility coefficient, $A$ is the upstream drainage area, $S$ is the slope, $m_e$ and $n_e$ are
parameters that should be chosen to constrain the ratio $m_e/n_e$ between 0.35 and 0.8 \citep{Croissant2014,Ueda2015,Beucher2020}, $G$ is the dimensionless
deposition/transport coefficient for the enriched stream power law and $K_d$ is the effective diffusivity. Terms $$K_f A^{m_e}S^{n_e}$$ and $$K_d \bm{\nabla}^2 h$$
consider long-range processes described by a stream power law equation \citep{Tucker1999,Ueda2015,Beucher2020} and short-range processes are
proportional to slope \citep{Burov1997,Ueda2015,Beucher2020}.

>>>>

\section{Erosion and sedimentation}\label{sec:erosion}
Surface processes at either the lithosphere-air interface or in correspondence of the free surface have been implemented by means of the software
Fastscape\footnote{\url{https://fastscape.org/}} \citep{Braun2013,Cordonnier2019,Yuan2019a,Yuan2019b}. FastScapeLib is a set of routines that solve the stream
power law (enriched by a sediment transport/deposition term) \citep{Yuan2019a}, hillslope diffusion and marine transport and deposition \citep{Yuan2019b}.
The partial differential equation solved by FastScapeLib is:
\begin{equation}
\frac{\partial h}{ \partial t}=U-K_f A^{m_e}S^{n_e} + \frac{G}{A}\int_A \left( U-\frac{\partial h}{\partial t} \right) dA + K_d \bm{\nabla}^2 h 
\end{equation}
where $h$ is the topography, $U$ is the uplift, $K_f$ is the erodibility coefficient, $A$ is the upstream drainage area, $S$ is the slope, $m_e$ and $n_e$ are
parameters that should be chosen to constrain the ratio $m_e/n_e$ between 0.35 and 0.8 \citep{Croissant2014,Ueda2015,Beucher2020}, $G$ is the dimensionless
deposition/transport coefficient for the enriched stream power law and $K_d$ is the effective diffusivity. Terms $K_f A^{m_e}S^{n_e}$ and $K_d \bm{\nabla}^2 h$
consider long-range processes described by a stream power law equation \citep{Tucker1999,Ueda2015,Beucher2020} and short-range processes are
proportional to slope \citep{Burov1997,Ueda2015,Beucher2020}.

### 2022-01-28 .debris/2022-01-27 14.30.56.00/Paper.tex
modified

\section{Introduction}\label{sec:intro}
This document includes a description of the code FALCON, with a presentation of the features implemented followed by results of extensive benchmarks listed in
Table \ref{tab:list}, implemented to verify that the code solves correctly a large range of problems. Description and results of all benchmarks are shown
in Section \ref{sec:benchmark}.

>>>>

\section{Introduction}\label{sec:intro}
This document includes a description of the code FALCON, with a presentation of the features implemented followed by results of extensive benchmarks listed in
Table \ref{tab:list}, performed to verify that the code solves correctly a large range of problems. Description and results of all benchmarks are shown
in Section \ref{sec:benchmark}.

### 2022-01-28 .debris/2022-01-27 14.32.17.00/Paper.tex
modified

\section{Introduction}\label{sec:intro}
This document includes a description of the code FALCON, with a presentation of the features implemented followed by results of extensive benchmarks listed in
Table \ref{tab:list}, performed to verify that the code solves correctly a large range of problems. Description and results of all benchmarks are shown
in Section \ref{sec:benchmark}.

\begin{table}[H]
\caption{List of benchmarks implemented for each feature of the code. Data of all benchmarks can be found at 
\url{https://github.com/aleregorda/Benchmarks}}
\centering
\begin{tabular}{| l | l | l |}
\toprule
 \textbf{Feature}  & \textbf{Benchmark} & \textbf{Section} \\
\midrule
  Solver  & Stokes flow & \ref{sec:stokes} \\
\hline
  \multirow{2}{*}{Markers advection} & Zalesak disk & \ref{sec:runge} \\
    & Conservative Interpolation Velocity & \ref{sec:CVI} \\
\hline
  \multirow{4}{*}{Momentum equation}  & Poiseuille flow & \ref{sec:poiseuille}\\
    & Instantaneous 2D sphere & \ref{sec:ist_sphere} \\
    & Rayleigh-Taylor experiment & \ref{sec:rayleigh} \\
    & Falling block & \ref{sec:block} \\
\hline
    & 2D Stokes sphere & \ref{sec:sphere} \\
    Sticky air and  & Stabilisation algorithm & \ref{sec:stab} \\
    free surface & Topography relaxation & \ref{sec:crameri} \\
  & Spontaneous subduction & \ref{sec:subduction} \\
\hline
  Erosion and sedimentation  & - & - \\
\hline
   Non-linear  & Slab detachment & \ref{sec:slab} \\
   visco-plasticity & Indenter & \ref{sec:indenter} \\
    & Brick & \ref{sec:brick} \\
\hline
  \multirow{3}{*}{Energy equation}  & Advection stabilisation & \ref{sec:advection} \\
    & Simple shear heating & \ref{sec:simple_shear} \\
    & Shear and adiabatic heating & \ref{sec:shear} \\
\hline
\multirow{3}{*}{Energy + momentum} & Mantle convection & \ref{sec:mantle} \\
& Viscoplastic mantle convection & \ref{sec:visco_mantle} \\
& Thin layer entrainment & \ref{sec:thin} \\
\hline
  Phase changes  & \multirow{2}{*}{Hydrated sinking cylinder} & \multirow{2}{*}{\ref{sec:quinquis}} \\
  and hydration  &  & \\
\hline
  Melting & Experimental melting curves & \ref{sec:katz} \\
\bottomrule
\end{tabular}
\label{tab:list}
\end{table}

>>>>

\section{Introduction}\label{sec:intro}
This document includes a description of the code FALCON, with a presentation of the features implemented followed by results of extensive benchmarks listed in
Table \ref{tab:list}, performed to verify that the code solves correctly a wide range of problems. Description and results of all benchmarks are shown
in Section \ref{sec:benchmark}.

\begin{table}[H]
\caption{List of benchmarks performed for each feature of the code. Data of all benchmarks can be found at 
\url{https://github.com/aleregorda/Benchmarks}}
\centering
\begin{tabular}{| l | l | l |}
\toprule
 \textbf{Feature}  & \textbf{Benchmark} & \textbf{Section} \\
\midrule
  Solver  & Stokes flow & \ref{sec:stokes} \\
\hline
  \multirow{2}{*}{Markers advection} & Zalesak disk & \ref{sec:runge} \\
    & Conservative Interpolation Velocity & \ref{sec:CVI} \\
\hline
  \multirow{4}{*}{Momentum equation}  & Poiseuille flow & \ref{sec:poiseuille}\\
    & Instantaneous 2D sphere & \ref{sec:ist_sphere} \\
    & Rayleigh-Taylor experiment & \ref{sec:rayleigh} \\
    & Falling block & \ref{sec:block} \\
\hline
    & 2D Stokes sphere & \ref{sec:sphere} \\
    Sticky air and  & Stabilisation algorithm & \ref{sec:stab} \\
    free surface & Topography relaxation & \ref{sec:crameri} \\
  & Spontaneous subduction & \ref{sec:subduction} \\
\hline
  Erosion and sedimentation  & - & - \\
\hline
   Non-linear  & Slab detachment & \ref{sec:slab} \\
   visco-plasticity & Indenter & \ref{sec:indenter} \\
    & Brick & \ref{sec:brick} \\
\hline
  \multirow{3}{*}{Energy equation}  & Advection stabilisation & \ref{sec:advection} \\
    & Simple shear heating & \ref{sec:simple_shear} \\
    & Shear and adiabatic heating & \ref{sec:shear} \\
\hline
\multirow{3}{*}{Energy + momentum} & Mantle convection & \ref{sec:mantle} \\
& Viscoplastic mantle convection & \ref{sec:visco_mantle} \\
& Thin layer entrainment & \ref{sec:thin} \\
\hline
  Phase changes  & \multirow{2}{*}{Hydrated sinking cylinder} & \multirow{2}{*}{\ref{sec:quinquis}} \\
  and hydration  &  & \\
\hline
  Melting & Experimental melting curves & \ref{sec:katz} \\
\bottomrule
\end{tabular}
\label{tab:list}
\end{table}

### 2022-01-28 .debris/2022-01-27 14.33.22.00/Paper.tex
modified

\section{Erosion and sedimentation}\label{sec:erosion}
Surface processes at either the lithosphere-air interface or in correspondence of the free surface have been implemented by means of the software
Fastscape\footnote{\url{https://fastscape.org/}} \citep{Braun2013,Cordonnier2019,Yuan2019a,Yuan2019b}. FastScapeLib is a set of routines that solve the stream
power law (enriched by a sediment transport/deposition term) \citep{Yuan2019a}, hillslope diffusion and marine transport and deposition \citep{Yuan2019b}.
The partial differential equation solved by FastScapeLib is:
\begin{equation}
\frac{\partial h}{ \partial t}=U-K_f A^{m_e}S^{n_e} + \frac{G}{A}\int_A \left( U-\frac{\partial h}{\partial t} \right) dA + K_d \bm{\nabla}^2 h 
\end{equation}
where $h$ is the topography, $U$ is the uplift, $K_f$ is the erodibility coefficient, $A$ is the upstream drainage area, $S$ is the slope, $m_e$ and $n_e$ are
parameters that should be chosen to constrain the ratio $m_e/n_e$ between 0.35 and 0.8 \citep{Croissant2014,Ueda2015,Beucher2020}, $G$ is the dimensionless
deposition/transport coefficient for the enriched stream power law and $K_d$ is the effective diffusivity. Terms $K_f A^{m_e}S^{n_e}$ and $K_d \bm{\nabla}^2 h$
consider long-range processes described by a stream power law equation \citep{Tucker1999,Ueda2015,Beucher2020} and short-range processes are
proportional to slope \citep{Burov1997,Ueda2015,Beucher2020}.

>>>>

\section{Erosion and sedimentation}\label{sec:erosion}
Surface processes at either the lithosphere-air interface or in correspondence of the free surface have been implemented by means of the software
Fastscape\footnote{\url{https://fastscape.org/}} \citep{Braun2013,Cordonnier2019,Yuan2019a,Yuan2019b}. FastScapeLib\footnote{\url{https://fastscape.org/}}
is a set of routines that solve the stream power law (enriched by a sediment transport/deposition term) \citep{Yuan2019a}, hillslope diffusion and marine
transport and deposition \citep{Yuan2019b}. The partial differential equation solved by FastScapeLib\footnote{\url{https://fastscape.org/}} is:
\begin{equation}
\frac{\partial h}{ \partial t}=U-K_f A^{m_e}S^{n_e} + \frac{G}{A}\int_A \left( U-\frac{\partial h}{\partial t} \right) dA + K_d \bm{\nabla}^2 h 
\end{equation}
where $h$ is the topography, $U$ is the uplift, $K_f$ is the erodibility coefficient, $A$ is the upstream drainage area, $S$ is the slope, $m_e$ and $n_e$ are
parameters that should be chosen to constrain the ratio $m_e/n_e$ between 0.35 and 0.8 \citep{Croissant2014,Ueda2015,Beucher2020}, $G$ is the dimensionless
deposition/transport coefficient for the enriched stream power law and $K_d$ is the effective diffusivity. Terms $K_f A^{m_e}S^{n_e}$ and $K_d \bm{\nabla}^2 h$
consider long-range processes described by a stream power law equation \citep{Tucker1999,Ueda2015,Beucher2020} and short-range processes are
proportional to slope \citep{Burov1997,Ueda2015,Beucher2020}.

### 2022-01-28 .debris/2022-01-27 15.12.43.00/Paper.tex
modified

\section{Erosion and sedimentation}\label{sec:erosion}
Surface processes at either the lithosphere-air interface or in correspondence of the free surface have been implemented by means of the software
Fastscape\footnote{\url{https://fastscape.org/}} \citep{Braun2013,Cordonnier2019,Yuan2019a,Yuan2019b}. FastScapeLib is a set of routines that solve the stream
power law (enriched by a sediment transport/deposition term) \citep{Yuan2019a}, hillslope diffusion and marine transport and deposition \citep{Yuan2019b}.
The partial differential equation solved by FastScapeLib is:
\begin{equation}
\frac{\partial h}{ \partial t}=U-K_f A^{m_e}S^{n_e} + \frac{G}{A}\int_A \left( U-\frac{\partial h}{\partial t} \right) dA + K_d \bm{\nabla}^2 h 
\end{equation}
where $h$ is the topography, $U$ is the uplift, $K_f$ is the erodibility coefficient, $A$ is the upstream drainage area, $S$ is the slope, $m_e$ and $n_e$ are
parameters that should be chosen to constrain the ratio $m_e/n_e$ between 0.35 and 0.8 \citep{Croissant2014,Ueda2015,Beucher2020}, $G$ is the dimensionless
deposition/transport coefficient for the enriched stream power law and $K_d$ is the effective diffusivity. Terms $K_f A^{m_e}S^{n_e}$ and $K_d \bm{\nabla}^2 h$
consider long-range processes described by a stream power law equation \citep{Tucker1999,Ueda2015,Beucher2020} and short-range processes are
proportional to slope \citep{Burov1997,Ueda2015,Beucher2020}.

>>>>

\section{Erosion and sedimentation}\label{sec:erosion}
Surface processes at either the lithosphere-air interface or in correspondence of the free surface have been implemented by means of the software
Fastscape\footnote{\url{https://fastscape.org/}} \citep{Braun2013,Cordonnier2019,Yuan2019a,Yuan2019b}. FastScapeLib is a set of routines that solve the stream
power law (enriched by a sediment transport/deposition term) \citep{Yuan2019a}, hillslope diffusion and marine transport and deposition \citep{Yuan2019b}.
The partial differential equation solved by FastScapeLib is:
\begin{equation}
\frac{\partial h}{ \partial t}=U-K_f A^{m_e}S^{n_e} + \frac{G}{A}\int_A \left( U-\frac{\partial h}{\partial t} \right) dA + K_d \bm{\nabla}^2 h 
\end{equation}
where $h$ is the topography, $U$ is the uplift, $K_f$ is the erodibility coefficient, $A$ is the upstream drainage area, $S$ is the slope, $m_e$ and $n_e$ are
parameters that should be chosen to constrain the ratio $m_e/n_e$ between 0.35 and 0.8 \citep{Croissant2014,Ueda2015,Beucher2020}, $G$ is the dimensionless
deposition/transport coefficient for the enriched stream power law and $K_d$ is the effective diffusivity. Terms $K_f A^{m_e}S^{n_e}$ and $K_d \bm{\nabla}^2 h$
consider long-range processes, described by a stream power law equation \citep{Tucker1999,Ueda2015,Beucher2020}, and short-range processes,
proportional to slope \citep{Burov1997,Ueda2015,Beucher2020}.
